Exploiting Array Syntax in Fortran for Accelerator Programming\footnote*{Foo!}

### 2010-12-19 opencl/papers/programming-model.tex
Spelling

Note that while {\tt foo} is defined in terms of purely scalar
quantities, it can be \emph{applied} to arrays as shown.  While this
may seem like a trivial example, such simple functions may be composed
with other elemental functions to perform powerful computations,
especially when applied to arrays.  Our prototype tool transforms
elemental functions to inline OpenCL functions.  Thus there is no
penalty for usage of elemental functions and they provide a convient
mechanism to express algorithms in simpler segments.

@@

A kernel procedure (specified by the {\tt \!\$OFP KERNEL} directive) must be
pure and all array variables must be declared as contiguous.  A kernel
procedure may not call other procedures except for limited intrisic
functions (primarily math), user-defined elemental function, and the
{\tt interior} and {\tt region} functions.  We plan to address
non-contiguous arrays (such as those that result from strided access)
by mapping array strides to gather/scatter-style memory accessors.

>>>>

Note that while {\tt foo} is defined in terms of purely scalar
quantities, it can be \emph{applied} to arrays as shown.  While this
may seem like a trivial example, such simple functions may be composed
with other elemental functions to perform powerful computations,
especially when applied to arrays.  Our prototype tool transforms
elemental functions to inline OpenCL functions.  Thus there is no
penalty for usage of elemental functions and they provide a convenient
mechanism to express algorithms in simpler segments.

@@

A kernel procedure (specified by the {\tt \!\$OFP KERNEL} directive) must be
pure and all array variables must be declared as contiguous.  A kernel
procedure may not call other procedures except for limited intrinsic
functions (primarily math), user-defined elemental function, and the
{\tt interior} and {\tt region} functions.  We plan to address
non-contiguous arrays (such as those that result from strided access)
by mapping array strides to gather/scatter-style memory accessors.

### 2010-12-19 opencl/papers/source-to-source.tex
Spelling

An important concept in OpenCL is that of a thread and a thread group.  Thread
groups are used to run an OpenCL kernel concurrently on several processor
elements on the OpenCL device (often a GPU).  Consider a data-parallel
statement written in terms of an elemental fuction as discussed above.  The
act of running an OpenCL kernel can be thought of as having a particular
thread assigned to each instance of the call to the elemental function as it
is mapped across the arrays in the data-parallel statement.  In practice,
these threads are packaged into thread groups when they are run on the device
hardware.

@@

This sections outlines the OpenCL equivalent syntax for portions of
the Fortran shallow-water code described in
Section~\ref{sec:shallow-water}.  The notation uses uppercase for
arrays and lowercase for scalar quantities.  Interior variables are
denoted by an {\tt i} preceeding the array name.  For example, {\tt iH =
  interior(H, halo)} is a local copy of interior region of array {\tt
  H} (representing height) in the shallow water model.

>>>>

An important concept in OpenCL is that of a thread and a thread group.  Thread
groups are used to run an OpenCL kernel concurrently on several processor
elements on the OpenCL device (often a GPU).  Consider a data-parallel
statement written in terms of an elemental function as discussed above.  The
act of running an OpenCL kernel can be thought of as having a particular
thread assigned to each instance of the call to the elemental function as it
is mapped across the arrays in the data-parallel statement.  In practice,
these threads are packaged into thread groups when they are run on the device
hardware.

@@

This sections outlines the OpenCL equivalent syntax for portions of
the Fortran shallow-water code described in
Section~\ref{sec:shallow-water}.  The notation uses uppercase for
arrays and lowercase for scalar quantities.  Interior variables are
denoted by an {\tt i} preceding the array name.  For example, {\tt iH =
  interior(H, halo)} is a local copy of interior region of array {\tt
  H} (representing height) in the shallow water model.
